---
title: "Your Title Comes Here"
subtitle: "Subtitle Comes Here"
author: "Student(s) Names and Student ID's Come Here"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output:
  slidy_presentation:
    font_adjustment: 0
    highlight: haddock
    mathjax: "default"
    df_print: paged
---

```{r setup, include=FALSE}
# Use this chunk to quietly load your pacakges

knitr::opts_chunk$set(
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
# Packages loaded in this chunk will not appear in the presentation. 

library(ggplot2) # Useful for creating plots
library(dplyr)  # Useful for data maipulation
library(knitr) # Useful for creating nice tables

```


# RPubs link information

- You must publish your presentation to RPubs (see [here](https://astral-theory-157510.appspot.com/secured/RBootcamp_Course_04.html#creating_an_r_markdown_document_in_r_studio)) and add this link to your presentation here.

- Rpubs link comes here: www.........

- This online version of the presentation will be used for marking. Failure to add your link will delay your feedback and risk late penalties.

# Introduction

- The following link will help you with creating R Markdown Slidy Presentations
- http://rmarkdown.rstudio.com/slidy_presentation_format.html
- Don't forget about [Bootcamp 4](https://astral-theory-157510.appspot.com/secured/RBootcamp_Course_04.html)
- A good introduction provides a brief background to the problem, defines important terms, and leads to a strong rationale. 

# Introduction Cont.

- Keep everything short and straight to the point. 
- Use bullet points to help minimise text.
- Add relevant images to make your presentation more appealing
- Remember, you have a maximum of 20 slides to fit everything in.
- Ensure each slide fits on one screen. The reader should not have to scroll down. 


# Problem Statement

- State the overall problem/question driving the investigation
- Summarise how you will use statistics to solve the problem or answer your question.

# Data

- You can use multiple slides to break up your sections. 
- Explain how you collected your data.
- There should be enough detail here so that someone else could replicate your data collection.
- Explain the sampling method if known
- Ensure you reference the data source if you have used Open Data


# Data Cont.

- List and explain the important variables. 
- If you have factors, explain each level.
- Explain the scale of numeric variables.
- Justify everything that you do to preprocess the data.

```{r}

Unemployement_male <- read.csv("indicator_f 25-54 unemploy.csv")


```

# Descriptive Statistics and Visualisation

- Summarise the important variables in your investigation.
- Use visualisation to highlight interesting features of the data and tell the overall story.
- Explain how you dealt with data issues (if any), e.g. missing data and outliers.
- Here are the examples of R chunks and outputs

```{r}
plot(Sepal.Length ~ Petal.Length, data = iris)
```

# Decsriptive Statistics Cont.

- You can use the `knitr:kable` function to print nice HTML tables. Here is an example R code:

```{r}
iris %>% group_by(Species) %>% summarise(Min = min(Petal.Length,na.rm = TRUE),
                                           Q1 = quantile(Petal.Length,probs = .25,na.rm = TRUE),
                                           Median = median(Petal.Length, na.rm = TRUE),
                                           Q3 = quantile(Petal.Length,probs = .75,na.rm = TRUE),
                                           Max = max(Petal.Length,na.rm = TRUE),
                                           Mean = mean(Petal.Length, na.rm = TRUE),
                                           SD = sd(Petal.Length, na.rm = TRUE),
                                           n = n(),
                                           Missing = sum(is.na(Petal.Length))) -> table1
knitr::kable(table1)
```


# Hypothesis Testing

- Apply an appropriate hypothesis test for your investigation. 
- Ensure you state and check any assumptions. 
- Report the appropriate values and interpret the results.
- Here is an example:

```{r}
model1 <- lm(Sepal.Length ~ Petal.Length, data = iris)
model1 %>% summary()
```

# Hypthesis Testing Cont.

- Here are the examples of mathematical equations:

$$H_0: \mu_1 = \mu_2 $$

$$H_A: \mu_1 \ne \mu_2$$

$$S = \sum^n_{i = 1}d^2_i$$

- You can also place equations inline: $z = \frac{x - \mu}{\sigma}$

# Discussion

- Discuss the major findings of your investigation
- Discuss any strengths and limitations. 
- Propose directions for future investigations. 
- This is a good place to re-state your findings as a final conclusion. What is the one take home message the reader should leave with?
- Your final conclusion needs to be very clear.

# References

- Provide a list of any references you use in the presentation. 